Equations & R Code

### 2017-03-08 manuscript/coexistence-stability_SI.Rmd
fixes small typos

Condition 1 is already included in our main analysis (Figures 2 and 4).
Condition 2 simply creates conditions where some species cannot coexist, which would not change the relationship between species richness and ecosystem variability, but rather disallow it.
Condition 3 is more interesting, because it could create situations where species may not coexist, but it could also weaken the diversity--ecosystem variabilty relationship be reducing mean biomass and the effect of species with very nonlinear growth rates.
To explore the effect of condition 3, we ran simulations across a gradient of resource variability (11 levels) crossed with a gradient of mean resource levels (4 levels: $\mu_R = 1,2,3,4$).

As expected, lower mean levels of resource make coexistence more difficult because resource acquisitive species are never favored (Fig. S1-x).
Our general conclusion remains, however, that positive diversity--ecosystem variability relationships are possible.
However, the occurence a of positive diversity--ecosystem variability relationship depends on amount of resource variability being sampled over and the traits of individual species (e.g., resource uptake curves). 
In other words, the patterns we report in the main text require that species coexistence be possible given the environmental conditions.

@@

From one to four species, the relationship is as presented in the main text: total community *CV* increases approximately linearly with environmental variability because (1) environmental variability promotes species coexistence \emph{and} (2) environmental variability causes populations fluctuations to increase (Figure S1-x).
However, after four species, the relationship saturates --- species additions due to coexistence by the storage effect completely buffer ecosystem variability from further increases in environmental variability (Figure S1-x).
Thus, our results provide novel theoretical explanations for positive and flat diversity--ecosystem variability relationships.

>>>>

Condition 1 is already included in our main analysis (Figures 2 and 4 in the main text).
Condition 2 simply creates conditions where some species cannot coexist, which would not change the relationship between species richness and ecosystem variability, but rather disallow it.
Condition 3 is more interesting, because it could create situations where species may not coexist, but it could also weaken the diversity--ecosystem variabilty relationship be reducing mean biomass and the effect of species with very nonlinear growth rates.
To explore the effect of condition 3, we ran simulations across a gradient of resource variability (11 levels) crossed with a gradient of mean resource levels (4 levels: $\mu_R = 1,2,3,4$).

As expected, lower mean levels of resource make coexistence more difficult because resource acquisitive species are never favored (Fig. S1-3).
Our general conclusion remains, however, that positive diversity--ecosystem variability relationships are possible.
However, the occurence a of positive diversity--ecosystem variability relationship depends on amount of resource variability being sampled over and the traits of individual species (e.g., resource uptake curves). 
In other words, the patterns we report in the main text require that species coexistence be possible given the environmental conditions.

@@

From one to four species, the relationship is as presented in the main text: total community *CV* increases approximately linearly with environmental variability because (1) environmental variability promotes species coexistence \emph{and} (2) environmental variability causes populations fluctuations to increase (Figure S1-4).
However, after four species, the relationship saturates --- species additions due to coexistence by the storage effect completely buffer ecosystem variability from further increases in environmental variability (Figure S1-4).
Thus, our results provide novel theoretical explanations for positive and flat diversity--ecosystem variability relationships.

### 2017-03-08 manuscript/coexistence-stability_SI.tex
fixes small typos

Condition 1 is already included in our main analysis (Figures 2 and 4).
Condition 2 simply creates conditions where some species cannot coexist,
which would not change the relationship between species richness and
ecosystem variability, but rather disallow it. Condition 3 is more
interesting, because it could create situations where species may not
coexist, but it could also weaken the diversity--ecosystem variabilty
relationship be reducing mean biomass and the effect of species with
very nonlinear growth rates. To explore the effect of condition 3, we
ran simulations across a gradient of resource variability (11 levels)
crossed with a gradient of mean resource levels (4 levels:
\(\mu_R = 1,2,3,4\)).

As expected, lower mean levels of resource make coexistence more
difficult because resource acquisitive species are never favored (Fig.
S1-x). Our general conclusion remains, however, that positive
diversity--ecosystem variability relationships are possible. However,
the occurence a of positive diversity--ecosystem variability
relationship depends on amount of resource variability being sampled
over and the traits of individual species (e.g., resource uptake
curves). In other words, the patterns we report in the main text require
that species coexistence be possible given the environmental conditions.

@@

From one to four species, the relationship is as presented in the main
text: total community \emph{CV} increases approximately linearly with
environmental variability because (1) environmental variability promotes
species coexistence \emph{and} (2) environmental variability causes
populations fluctuations to increase (Figure S1-x). However, after four
species, the relationship saturates --- species additions due to
coexistence by the storage effect completely buffer ecosystem
variability from further increases in environmental variability (Figure
S1-x). Thus, our results provide novel theoretical explanations for
positive and flat diversity--ecosystem variability relationships.

>>>>

Condition 1 is already included in our main analysis (Figures 2 and 4 in
the main text). Condition 2 simply creates conditions where some species
cannot coexist, which would not change the relationship between species
richness and ecosystem variability, but rather disallow it. Condition 3
is more interesting, because it could create situations where species
may not coexist, but it could also weaken the diversity--ecosystem
variabilty relationship be reducing mean biomass and the effect of
species with very nonlinear growth rates. To explore the effect of
condition 3, we ran simulations across a gradient of resource
variability (11 levels) crossed with a gradient of mean resource levels
(4 levels: \(\mu_R = 1,2,3,4\)).

As expected, lower mean levels of resource make coexistence more
difficult because resource acquisitive species are never favored (Fig.
S1-3). Our general conclusion remains, however, that positive
diversity--ecosystem variability relationships are possible. However,
the occurence a of positive diversity--ecosystem variability
relationship depends on amount of resource variability being sampled
over and the traits of individual species (e.g., resource uptake
curves). In other words, the patterns we report in the main text require
that species coexistence be possible given the environmental conditions.

@@

From one to four species, the relationship is as presented in the main
text: total community \emph{CV} increases approximately linearly with
environmental variability because (1) environmental variability promotes
species coexistence \emph{and} (2) environmental variability causes
populations fluctuations to increase (Figure S1-4). However, after four
species, the relationship saturates --- species additions due to
coexistence by the storage effect completely buffer ecosystem
variability from further increases in environmental variability (Figure
S1-4). Thus, our results provide novel theoretical explanations for
positive and flat diversity--ecosystem variability relationships.
